---
title: "cncwithalarm from Apr 18th to Apr 29th"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#import data
```{r include=FALSE}
#Sys.setlocale('LC_CTYPE', locale = "English_United States.1252") 
library(tidyverse)
library(plotly)
library(readxl)
cncwithalarm<- read_excel('cncdatawithalarm.xlsx')
```

#format data
```{r}
col_factor<-c('dSn','Status','Category','CurrenttoolNo','AMsgContent','AMsgNo')
cncwithalarm[,col_factor]<-lapply(cncwithalarm[,col_factor], as.factor)
```
#order by timestamp
```{r}
cncwithalarm<-cncwithalarm[order(cncwithalarm$EventTime),]
```


#data summary
#msgno = 32; msg content=71
#abnormality found on data:
#1. eg: T04 Dao Jun Yi Chang ->Toolno = 4&5; same issue with other Dao Jun Yi chang
#2. 1 msgno ->multiple msg content eg: EX1003 ->急停，急停q
#3. 71 out of 33294 obs status ==1
###Data cleaning

```{r}
cncwithalarm<-cncwithalarm[-4]
cont<-unique(cncwithalarm$AMsgContent) 
No<-unique(cncwithalarm$AMsgNo)
cncwithalarm$AMsgContent<-str_trim(cncwithalarm$AMsgContent)
```
#To explore msgno and msg content

```{r}
msg<-select(cncwithalarm,AMsgContent,AMsgNo)%>%group_by(AMsgNo,AMsgContent)%>%mutate(count=n())
msg1u<-unique(msg)
msg1u<-msg1u[order(msg1u$AMsgNo),]
write_excel_csv(msg1u,'AlarmMsgTable.csv')
```

#To clean wierd characters in alarm content
#MC3001 ->multiple alarm types
#EX1003	急停,急停q
#EX1012	处在换刀区域内,处在换刀区域内 <


```{r}
cncwithalarm$AMsgContent_cat<-NA
matchtable<-read_excel('Alarm_MatchTable.xlsx')
#To clean unique pair
alarmNo<-unique(matchtable$AMsgNo)
single_alarm<-alarmNo[alarmNo!='MC3001']

for (i in single_alarm){
  cncwithalarm$AMsgContent_cat[cncwithalarm$AMsgNo ==i]<-matchtable$`Alarm Category(CHN)`[matchtable$AMsgNo==i]
}


NA_sub<-cncwithalarm[is.na(cncwithalarm$AMsgContent_cat),]
```

#clean 1- multi alarm pair
#MC3001,MC3050,OT500, SV476,SV494

```{r}
MC3001_alarm<-unique(cncwithalarm$AMsgContent[cncwithalarm$AMsgNo=='MC3001'])

for (j in MC3001_alarm){
  if (any(matchtable$AMsgContent==j)){
  cncwithalarm$AMsgContent_cat[cncwithalarm$AMsgNo =='MC3001'&cncwithalarm$AMsgContent==j]<-unique(matchtable$`Alarm Category(CHN)`[matchtable$AMsgContent==j])}else {
    cncwithalarm$AMsgContent_cat[cncwithalarm$AMsgNo =='MC3001'&cncwithalarm$AMsgContent==j]<-NA}
}

cncwithalarm$AMsgContent_cat[cncwithalarm$AMsgContent=='LOUJIAGONG']<-c('漏加工')


#easy ones, no need translation
multi_easy<-c('OT500','SV476','SV494')
for (i in multi_easy){
  cncwithalarm$AMsgContent_cleaned[cncwithalarm$AMsgNo==i]<-cncwithalarm$AMsgContent[cncwithalarm$AMsgNo==i]
}

```

#for Currenttoolno == 0
```{r}
cncwithalarm<-cncwithalarm[cncwithalarm$CurrenttoolNo!=0,]

```



##1. plot the alarm distribution
```{r}
p1 <-ggplot(cncwithalarm,aes(x=fct_infreq(AMsgContent_cat)))+geom_bar()+theme(axis.text.x = element_text(size=5,angle = 90,colour = "red"))
 ggplotly(p1)
```
#1.1 Top 10 alarm pareto
```{r}
top_10<-cncwithalarm%>%group_by(AMsgContent_cat)%>%summarise(count=n())%>%arrange(desc(count))%>%top_n(10)

P1_1 <-cncwithalarm%>%filter(cncwithalarm$AMsgContent_cat %in% top_10$AMsgContent_cat)%>% ggplot(aes(x=fct_infreq(AMsgContent_cat)))+geom_bar()+theme(axis.text.x = element_text(size=8,angle = 90,colour = "red"))
ggplotly(P1_1)
```



#2. plot alarm vs currenttoolNo
#2.1 AmsgNo Vs CurrenttoolNo
```{r}
p2_1<-group_by(cncwithalarm,CurrenttoolNo,AMsgNo)%>%ggplot(aes(x=CurrenttoolNo, fill=AMsgNo))+geom_bar()+labs(x='Current tool no',y='alarm count', title='alarm distributio vs cutter no')
ggplotly(p2_1)
```
```{r}
df1<-group_by(cncwithalarm,CurrenttoolNo,AMsgNo)%>%
  summarise(count=n())%>%mutate(percentage=count/sum(count))

p2_2<-ggplot(df1,aes(x=CurrenttoolNo,y=count, fill=AMsgNo,order=percentage))+geom_bar(stat = 'identity')+geom_text(aes(label=round(percentage,2)),size=2)+labs(x='Current tool no',y='alarm count', title='alarm distributio vs cutter no')

ggplotly(p2_2)
```

#2.2 AmsgContent Vs CurrenttoolNo
```{r}
p2_3<-group_by(cncwithalarm,CurrenttoolNo,AMsgContent_cat)%>%ggplot(aes(x=CurrenttoolNo, fill=AMsgContent_cat))+geom_bar()+labs(x='Current tool no',y='alarm count', title='alarm distributio vs cutter no')
ggplotly(p2_3)
```
```{r}
df2<-group_by(cncwithalarm,CurrenttoolNo,AMsgContent_cleaned)%>%
  summarise(count=n())%>%mutate(percentage=count/sum(count))
p2_4<-
  ggplot(df2,aes(x=CurrenttoolNo,y=count, fill=AMsgContent_cleaned))+
  geom_bar(stat = 'identity')+
  #geom_text(aes(label=round(percentage,2)),vjust = 0, nudge_y = 15,size = 2,check_overlap = TRUE)+
  labs(x='Current tool No',y='Alarm Count', title='Alarm Distributio vs Cutter No')

ggplotly(p2_4)
```
Simplified alarm match table
```{r}
data3<-unique(matchtable[1:3])
write_excel_csv(data3,'Simplified_Alarm_Table.csv')
```

