---
title: "human analytics"
Author: Xiong Yuyu
output: html_document
---

Dataset
```{r include=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
data<-read_excel('EmployeeDetails_SHSSPL.xlsx')
```

Extract variables
```{r}
emp_data<-data%>%select(EmployeeID,EmploymentStatus,ResignationDate,ResignationReason,Position,SupervisorID,PersonnelAreaText,PersSubAreaText,EntryDate,LaborCategory,Gender,PermState,JobTitle,BirthDate,EducationalEstText)
```

Format Data

```{r}
#ID to char
emp_data[,c("EmployeeID","SupervisorID")]<-lapply(emp_data[,c("EmployeeID","SupervisorID")],as.character)

#Date to date
emp_data[,c("ResignationDate","EntryDate","BirthDate")]<-lapply(emp_data[,c("ResignationDate","EntryDate","BirthDate")],ymd)

#Factor
emp_data[,c( "EmploymentStatus","ResignationReason","Position","PersonnelAreaText","PersSubAreaText","LaborCategory","Gender","PermState","JobTitle","EducationalEstText")]<-lapply(emp_data[,c( "EmploymentStatus","ResignationReason","Position","PersonnelAreaText","PersSubAreaText","LaborCategory","Gender","PermState","JobTitle","EducationalEstText")], as.factor)
```

Understand Data

```{r}
summary(emp_data)

```

#CLEAN

```{r}
##
#unique(emp_data$EducationalEstText)
emp_data<-emp_data%>%filter(EducationalEstText%in%c('高中','大学 / 大专院校','中专','初中','中技','小学','Program Management Manager','Assistant Production Manager','Operations Configuration Specialist II'))

##filter NA
emp_data<-emp_data%>%filter_at(vars(Position,PermState,JobTitle,BirthDate),all_vars(!is.na(.)))

```

Feature Engineering

```{r}
emp_data["Status"]<-ifelse(emp_data$EmploymentStatus=="激活",0,1)

Today<-Sys.Date()
emp_data["Age"]<-time_length(interval(ymd(emp_data$BirthDate),ymd(Today)),"years")

emp_data["Tenure"]<-ifelse(emp_data$Status==1,time_length(interval(ymd(emp_data$EntryDate),ymd(emp_data$ResignationDate)),"years"),time_length(interval(ymd(emp_data$EntryDate),ymd(Today)),"years"))

emp_data<-emp_data%>% select(-c("EmploymentStatus","ResignationDate","EntryDate","BirthDate","Position","JobTitle"))

```

Exploration
1.turnover vs LaborCategory

```{r}

emp_data%>%
  group_by(LaborCategory)%>%
  summarise(turnover=mean(Status))%>%
  filter(turnover!=0)%>%
  ggplot(aes(x=LaborCategory,y=turnover))+geom_col()+geom_text(aes(label=round(turnover,2)))
emp_data%>%
  count(LaborCategory)%>%
  mutate(prop=n/sum(n))
```
2. Age and tenure turnover distribution
#20-35

```{r}
emp_data%>%subset(Status==1& LaborCategory=='DL')%>%
  ggplot(aes(x=Age))+
  geom_histogram(breaks=seq(10,65,by=5),col="#009E73",aes(fill=..count..))+
  scale_fill_gradient(low="green",high = "#009E73")+
  labs(x='Age',y='Resignation Count')+
  ggtitle("DL Age Distribution")+theme(plot.title = element_text(hjust = 0.5))

emp_data$churn<-factor(emp_data$Status,levels = c(0,1), 
                  labels = c('激活','离职'))
emp_data%>%subset(LaborCategory=='DL')%>%
  ggplot(aes(x=Tenure))+
  geom_histogram(fill=I("#009E73"),col=I("blue"),breaks=seq(0,ceiling(max(emp_data$Tenure)),by=1))+
  labs(x='Tenure',y='Count of Employees',title = "Tenure Distribution")+
  theme(plot.title = element_text(hjust = 0.5))+
  facet_grid(churn~.)
    
```

3.EducationalEstText
```{r}
emp_data%>%
  subset(Status==1)%>%
  ggplot(aes(x=EducationalEstText))+geom_bar()+geom_text(stat = 'count',aes(label=..count..),vjust=-0.5)
```

#Calculate information value
#< 0.15 Poor
#>0.15 and <0.4 Moderate
#> 0.4 Strong

```{r include=FALSE}
#install.packages('Information')
library(Information)
```
```{r}
info<-create_infotables(data=emp_data,y='Status')
info$Summary
feature<-subset(info$Summary,info$Summary$IV>0.15)[[1]]
data_final<-emp_data%>%select(feature, Status,-SupervisorID)
```
```{r}
data_final$Status<-as.factor(data_final$Status)
ggplot(data = data_final,aes(x=Status))+geom_bar()+geom_text(stat = 'count',aes(label=..count..))
```
**Only 11.6% are resigned class, data very imbalanced to detect resigned**


#Model
1.Split Data
```{r include=FALSE}
#install.packages('caret')
library('caret')
```

```{r}
set.seed(223)
index_train<-createDataPartition(data_final$Status,p=.8, list = FALSE)
train_set<-data_final[index_train,]
test_set<-data_final[-index_train,]
down_train<-downSample(x=train_set[,-ncol(train_set)],y=train_set$Status)

```

```{r}
table(down_train$Class)
table(test_set$Status)

```

2.Train
2.1 simple
```{r}
simple<-glm(Status~Tenure,family = 'binomial',data=train_set)
summary(simple)
```
2.2 Multi
```{r}
multi<-glm(Status~.,family = 'binomial',data=train_set)
summary(multi)
```
#Final
```{r}
final<-glm(Status~Tenure+LaborCategory,family = 'binomial',data=train_set)
summary(final)
```
####Evaluation####
```{r}
predict_train<-predict(final,newdata=train_set,type="response")
hist(predict_train)
cut_off_50_train<-ifelse(predict_train>0.3,1,0)
table(cut_off_50_train,train_set$Status)
confusionMatrix(table(cut_off_50_train,train_set$Status))
```
#condition positive is status =0; TN rate only 0.57, too low.
#Adjusted cutline from 0.5 to 0.3,TNR changes to 0.85.
#Data not balanced, prediction spread not reaching 1


```{r}
predict_test<-predict(final,newdata=test_set,type="response")
hist(predict_test)
```

#Table
```{r}
cut_off_50_test<-ifelse(predict_test>0.3,1,0)
table(cut_off_50_test,test_set$Status)
confusionMatrix(table(cut_off_50_test,test_set$Status))
```
##Accuracy=(2144+259)/(2561)=93.87%, a bit overfitting

###Using downsampled train_set

```{r}
down_all<-glm(Class~Tenure,family='binomial',data=down_train)
summary(down_all)
```
```{r}
predict_DT<-predict(down_all,down_train, type='response')
hist(predict_DT)
cut_off<-ifelse(predict_DT>0.5,1,0)
confusionMatrix(table(cut_off,down_train$Class))
```
#Downsampling model on test dataset
```{r}
predict_TT<-predict(down_all,newdata = test_set,type='response')
cut_off_test<-ifelse(predict_TT>0.5,1,0)
hist(predict_TT)
confusionMatrix(table(cut_off_test,test_set$Status))
```
#accuracy is sacrificed with balanced data set model as less valuable features and smaller sample size.However,specificty is greatly imporved t 91.6%. Our model can detect the churn more accurately





#Predict Active employees
```{r}
active_emp<-filter(emp_data,Status==0)
active_emp['risk']<-predict(final,newdata = active_emp,type="response")
hist(active_emp$risk)
```
```{r}
active_emp%>%select(EmployeeID,risk)%>%top_n(5,wt=risk)
```





