---
title: "A0091878_XiongYuyu_Day2LogisticRegression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
pacman::p_load(tidyverse, caret, corrplot, caTools,knitr,car,
               ROCR,IRdisplay, e1071, earth,readxl,pROC)
```

Load Data
```{r}
setwd("~/Documents/BAP/Predictive analytics/Day2/bank marketing")
data<-read_excel('bank_data.xlsx')
head(data,2)
str(data)
```
Meta-data:
Input variables:
# bank client data:
1 - age (numeric)
2 - job : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
3 - marital : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
4 - education (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
5 - default: has credit in default? (categorical: 'no','yes','unknown')
6 - housing: has housing loan? (categorical: 'no','yes','unknown')
7 - loan: has personal loan? (categorical: 'no','yes','unknown')
# related with the last contact of the current campaign:
8 - contact: contact communication type (categorical: 'cellular','telephone') 
9 - month: last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')
10 - day_of_week: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')
11 - duration: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be **discarded** if the intention is to have a realistic predictive model.
# other attributes:
12 - campaign: number of contacts performed during this campaign and for this client (numeric, includes last contact)
13 - pdays: number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
14 - previous: number of contacts performed before this campaign and for this client (numeric)
15 - poutcome: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')


Output variable (desired target):
16 - y - has the client subscribed a term deposit? (binary: 'yes','no')

#Data Preparation

To discard duration based on meta_data description
```{r}
data$duration<-NULL
```

To change categorical values to factor

```{r}
colnames(data)
```

```{r}
cols<-c("job","marital","education","default","housing","loan","contact","day","month","poutcome",'y')

data[cols]<-lapply(data[cols],as.factor)
```
```{r}
summary(data)
```
```{r}
contrasts(data$y)
```
```{r}
data%>%
  group_by(y)%>%
  summarise(per=n()/nrow(data))%>%
  ggplot(aes(x=y,y=per,fill=y))+
  geom_bar(stat = 'identity')+
  geom_text(aes(label=round(per,2)),vjust=2)
```

Unbalanced no/yes class!

```{r}
cor(data[c(1,6,12,13,14)])
```

Numerical variables no strong correlations.
Let's try do modeling first...
# Modeling
split data
```{r}
set.seed(123)
split<-sample.split(data$y,SplitRatio = 0.8)
train<-data[split,]
test<-data[!split,]
```


Put everything inside model
```{r}
model<-glm(y~.,data=train,family = 'binomial')
summary(model)
```

```{r}
vif(model)
```
```{r}
model2<-step(model,trace = F)
summary(model2)
```
```{r}
vif(model2)
```
1. From above, the variables that matter: job,marital,education,balance,housing,load,contact,day,month,campaign,poutcome.

2. for numerical varaibles, vif are all acceptable.

```{r}
anova(model2,test = 'Chisq')
```
From Anova, we see model2 is doing better than null and each variable is significant.

```{r}
train_pred<-predict(model2,newdata = train,type='response')

```

To select best threshold based AUC

```{r}
ROCRpred = prediction(train_pred, train$y)
ROCRperf = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))
```

Thus the best threshold seems between 0.1 and 0.2. Here we use the yes/overall ratio
```{r}
threshold<-sum(train$y=='yes')/length(train$y)
p_class<-ifelse(train_pred>=threshold,1,0)

matrix<-table(p_class,train$y)
matrix
```




```{r}
accuracy_train<-sum(diag(matrix))/sum(matrix)
recall_train<-matrix[2,2]/sum(matrix[,2])
accuracy_train
recall_train
```

```{r}
pr<-prediction(p_class,train$y)
perf<-performance(pr,measure = "tpr",x.measure = "fpr")
auc(train$y,p_class)
plot(perf)
```
```{r}
varImp(model2)
```

#Apply model to test data
```{r}
pred_test<-predict(model2,newdata = test,type = 'response')
pclass_test<-ifelse(pred_test>=threshold,1,0)

```

```{r}
matrix_test<-table(pclass_test,test$y)
matrix_test
```


```{r}
accuracy_test<-sum(diag(matrix_test))/sum(matrix_test)
recall_test<-matrix_test[2,2]/sum(matrix_test[,2])
accuracy_test
recall_test
```

```{r}
pred = prediction(train_pred, train$y)
perfmance = performance( pred, "lift", "rpp" )
plot(perfmance, main="lift curve", xlab = 'Proportion of Customers (sorted prob)')
```
We can also use lift curve to make our contact strategy.
